\cvevent{Mar 2019 - Present}{Head of Algo Trading}{Smarkets - London -}{smarkets.com}

I manage the sport algorithmic trading division consisting of 12 engineers, 10 quants and 8 ops traders.

We market-make sporting events 24/7 using python, rust, react and many other open source technologies on a microservice driven architecture
deployed into Kubernetes clusters on AWS.

I'm part of the leadearship team with daily interactions with the CEO of the group based in LA.


\cvevent{2008 - Present}{CTO - Principal}{Quantmind - London -}{quantmind.com}

Consultant specializing in quantitative finance, data analytics, machine learning, visualisation, microservices, full stack technological solutions and continous deployment. CTO level services.

Clients: Roche, OneMarket, BAML, CleverTech, BMLL Technologies, Citigroup, Investec


\cvevent{Mar 2018 - Feb 2019}{CTO}{Lendingblock - London -}{lendingblock.com}

I engineered the creation of the first cloud platform for cross blockchain borrowing and lending
while managing an agile team of six in house engineers and four near shore consultants.

Loans in cryptocurrency collateralized by other cryptocurrencies.


\cvevent{Mar 2015 - Feb 2016}{CTO}{BMLL Technologies - London -}{bmlltech.com}

Consultant Chief Technology Officer at an early stage tech startup with the aim to build the development team and the technology product,
a cloud based platform for limit order book (LOB) data and analytics.

The dev team grew from four to ten engineers and a minimum viable product was on its way by the time a permanent CTO came on board.

\cvevent{Mar 2009 - Mar 2014}{Quant Developer - Director}{Citi - London -}{citigroup.com}

Development of a web-based solution for quantitative analysis of interest rate options strategies.

Working closely with the head of the exotic trading desk.

\cvevent{Mar 2008 - Sep 2007}{Fund Manager}{Investec Asset Management - London}{}

Creating a new Quantitative Hedge Fund product within an established Asset management firm.

I was part of a group of five where I was heading the technological and algorithmic part of the project.

\cvevent{May 2006 - Sep 2007}{HF Option Trader}{Ulpia - Lugano}{}

Trading in currency and currency options at a start-up Hedge Fund in Switzerland

\cvevent{Oct 2003 - Mar 2006}{HF Strategist}{JWM Partners - London}{}

Strategist in European Fixed Income and Forex volatility trading at a macro \& relative value Hedge Fund.

\cvevent{Apr 2000 - Aug 2003}{Quantitative Developer - Prop Trader}{Nomura - London}{}

Quantitative analyst/trader in propriety trading group. Researching and trading in Fixed Income.
