\cvevent{Aug 2020 - Present}{Tech Lead - Crypto currency OTC trading}{B2C2 - London -}{b2c2.com}

I lead a team responsible for the rest API,
backend data and streaming services, customers market risk and post-trade analysis.
We market make all crosses in over 30 crypto currencies.
My role is 70\% hands on coding and the remaining split
between managing a team of seven senior developers, plan/design new features and interact with ops and traders.

Working in python, typescript and rust on an AWS based infrastructure.

\cvevent{Mar 2019 - Jul 2020}{Head of Algo Trading}{Smarkets - London -}{smarkets.com}

I managed the sport algorithmic trading division consisting of over twenty engineers and ten operational traders.
We traded sporting events 24/7 using python, rust, react and many other open source technologies on a
microservice driven architecture on AWS.

I was part of the leadership team with daily interactions with all main stakeholders.

\cvevent{2008 - Present}{Software Development}{Quantmind - London -}{quantmind.com}

This is my consulting company which I use for contract roles in data analytics, machine learning, quantitative finance,
visualisation, microservices and full stack technological solutions. The main technologies are python, typescript, docker, aws.
Currently working on \textcolor{sectcol}{metablock.io}, a cloud infrastructure for trading bots.

    {\bf Past clients}: Roche, OneMarket, BAML, CleverTech, BMLL Technologies, Citigroup, Investec


\cvevent{Mar 2018 - Feb 2019}{CTO}{Lendingblock - London -}{lendingblock.com}

I engineered the creation of the first cloud platform for cross blockchain borrowing and lending
while managing an agile team of six in house engineers and four near shore consultants.

Loans in cryptocurrency collateralized by other cryptocurrencies.


\cvevent{Mar 2015 - Feb 2016}{Tech Lead}{BMLL Technologies - London -}{bmlltech.com}

Consultant Chief Technology Officer at an early stage tech startup with the aim to build the development team and the technology product,
a cloud based platform for limit order book (LOB) data and analytics.

The dev team grew from four to ten engineers and a minimum viable product was on its way by the time a permanent CTO came on board.

\cvevent{Mar 2009 - Mar 2014}{Quant Developer - Director}{Citi - London -}{citigroup.com}

Development of a web-based solution for quantitative analysis of interest rate options strategies.

Working closely with the head of the exotic trading desk.

\cvevent{Mar 2008 - Sep 2007}{Quant Developer}{Investec Asset Management - London}{}

Creating a new Quantitative Hedge Fund product within an established Asset management firm.

I was part of a group of five where I was implementing the technological and algorithmic part of the project.

\cvevent{May 2006 - Sep 2007}{HF Option Trader}{Ulpia - Lugano}{}

Trading in currency and currency options at a start-up Hedge Fund in Switzerland

\cvevent{Oct 2003 - Mar 2006}{Quant Developer - Strategiest}{JWM Partners - London}{}

Developing systematic strategies in European Fixed Income and Forex volatility trading at a macro \& relative value Hedge Fund.

\cvevent{Apr 2000 - Aug 2003}{Quant Developer - Prop Trader}{Nomura - London}{}

Quantitative analyst/trader in propriety trading group. Researching and trading in Fixed Income.
