\cvevent{2008 - Present}{Owner - Software Development}{quantmind.com}{London}
{\bf Intermittent Consulting Engagements}

Provides independent consulting for project-based roles in trading technology and algorithmic trading,
leveraging expertise in Rust, Python, quantitative finance and cloud computing.

{\it Technologies}: rust, python, typescript, aws

\cvevent{Oct 2023 - Jul 2025}{Lead Quant Dev}{Onyx Capital Group}{London}

Led a high performance team in designing, deploying, and managing scalable, low-latency infrastructure
for commodity electronic trading. Successfully delivered a single dealer platform
enabling internalization of hedging and external trading with clients.

{\it Technologies}: rust, python, azure

\cvevent{Aug 2022 - Jun 2023}{Lead Quant Dev - Crypto systematic trading}{byte-trading.com}{London}

Designed and implemented systematic trading technology for crypto exchanges,
including market-making algorithms and risk management strategies.
Built Rust-based exchange connectivity services and a high-performance trading engine,
utilizing Python for post-trade data analysis. Led a small team of quant developers.

{\it Technologies}: rust, python, typescript, aws

\cvevent{Aug 2020 - Aug 2022}{Head of Crypto OTC trading}{b2c2.com}{London}

Led a team responsible for the OTC platform consisting of rest APIs,
backend data, streaming services, customers market risk and post-trade analysis.

{\it Technologies}: python, rust, typescript, aws

\cvevent{Mar 2019 - Jul 2020}{Head of Algo Trading}{smarkets.com}{London}

Managed the sport algorithmic trading division consisting of over twenty engineers \& quant developers and ten operational traders.
Market making sporting events 24/7 on Smarkets exchange, providing over 80\% of total liquidity.
I was part of the leadership team with daily interactions with all main stakeholders.

{\it Technologies}: python, rust, typescript, aws

\cvevent{Mar 2018 - Feb 2019}{CTO}{lendingblock.com}{London}

Engineered the creation of the first cloud platform for cross blockchain borrowing and lending
while managing an agile team of six in house engineers and four near shore consultants.

{\it Technologies}: python, javascript, solidity, aws, Ethereum blockchain


\cvevent{Mar 2015 - Feb 2016}{CTO}{bmlltech.com}{London}

Chief Technology Officer at an early stage tech startup with the aim to build the development team and the technology product,
a cloud based platform for limit order book (LOB) data and analytics.

{\it Technologies}: python, javascript, aws

\cvevent{Mar 2009 - Mar 2014}{Quant Dev - Director}{citigroup.com}{London}

Development of a web-based solution for quantitative analysis of interest rate options strategies.
Working with the head of the exotic trading desk.

{\it Technologies}: python, javascript, C++

\cvevent{Mar 2008 - Sep 2007}{Quant Developer}{investec.com}{London}

Creating a new Quantitative Hedge Fund product within an established Asset management firm.
I was part of a group of five where I was implementing the technological and algorithmic part of the project.

{\it Technologies}: python

\cvevent{May 2006 - Sep 2007}{HF Option Trader}{Ulpia}{Lugano}

Trading in currency and currency options at a start-up Hedge Fund in Switzerland

{\it Technologies}: C\#

\cvevent{Oct 2003 - Mar 2006}{Quant Developer - Strategiest}{JWM Partners}{London}

Developing systematic strategies in European Fixed Income and Forex volatility trading at a macro \& relative value Hedge Fund.

{\it Technologies}: C\#

\cvevent{Apr 2000 - Aug 2003}{Quant Developer - Prop Trader}{Nomura}{London}

Quantitative analyst/trader in propriety trading group. Researching and trading in Fixed Income.

{\it Technologies}: C++
